---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# simpleweather

<!-- badges: start -->
[![R-CMD-check](https://github.com/joemarlo/simpleweather/workflows/R-CMD-check/badge.svg)](https://github.com/joemarlo/simpleweather/actions)
<!-- badges: end -->

simpleweather is an R package that simply retrieves daily weather data.

```{r example}
library(simpleweather)
dates <- Sys.Date() + -7:2
lat <- 40.7812
long <- -73.9665
get_weather(dates, lat, long)
```

## Installation and setup

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joemarlo/simpleweather")
```

Requires API keys for the [NOAA API](https://www.ncdc.noaa.gov/cdo-web/webservices/v2) and [OpenWeather API](https://openweathermap.org/api/one-call-api). You can request those keys for free [here](https://www.ncdc.noaa.gov/cdo-web/token) and [here](https://openweathermap.org/price). Historical NOAA weather data only available for the United States.

And then log your API keys via the set_api_key_* functions.

``` r
set_api_key_noaa("<token>")
set_api_key_openweather("<token>")
```

## Todo

- Remove `tibble` dependency
- Figure out how to run tests w/o explicit API key
- Double check documentation is correct of weather variables
- Implement rate limiting messages?
